Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-10-07 manuscript.Rmd

Beyond standard preregistrations in psychological research, we believe that two applications specifically lend themselves to PAC.
First, registrations of clinical trials typically describe analyses in exhaustive detail.
Those registrations typically contain a detailed description of how results will be presented, including example tables and graphics [@ICH1998].
PAC may significantly reduce the required workload while maintaining (and exceeding) the required standards for registering a clinical trial.

>>>>

Beyond standard preregistrations in psychological research, we believe that two applications specifically lend themselves to PAC.
First, pregistrations of clinical trials (there called statistical analysis plan, @ICH1998) typically describe analyses in exhaustive detail.
Those preregistrations typically contain a detailed description of how results will be presented, including shells of tables and graphics [@yuanGuideStatisticalAnalysis2019].
PAC may significantly reduce the required workload while maintaining (and exceeding) the required standards for preregistering a clinical trial.
